### 2020-03-10 manuscript/ERL_global_C_review.Rmd
minor edits

                  \usepackage{setspace}
                  \onehalfspacing

@@

Despite the centrality of forest C cycling in regulating both atmospheric CO~2~ and ecosystem function and diversity, we lack a comprehensive understanding of how C cycling varies with across biomes and with stand age. While satellite measurements are increasingly useful for global estimates of forest $GPP$ (Bagdley et al. 2019, [Li & Xiao 2019](https://www.mdpi.com/2072-4292/11/21/2563)), aboveground biomass ($B_{ag}$) (REFS), and possibly woody mortality (**?** *i.e.*, $B_{ag}$ losses to mortality $M_{woody}$) (REFS), the remainder of C fluxes and stocks can only be quantified by ground-based measurements. Moreover, data on stand characteristics--including species composition, age, and disturbance history--are critical to interpreting and projecting into the future, but [usually rely on ground-based measurements]. Thus, ground-based measurements are--and will continue to be--central to characterizing forest C cycling. Tens of thousands of forest C measurements have been published, but their distribution across literally thousands of scientific articles-- along with variation in data formats, units, measurement methods, *etc.*--have made them effectively inaccesible for many global-scale analyses, including those attempting to quantify the role of forests in the global C cycle (*e.g.*, Pan et al 2011), and model evaluation (Clark et al 2017, Luo et al 2012). Important progress has been made in synthesizing data to address how C cycling varies across forest biomes (Luyssaert et al. 2007; REFS) and stand ages (REFS), yet generally consider only a limited set of C variables (but see Anderson-Teixeira et al 2016 for the tropics) and do not consider age-by-biome interactions. To address the need for global-scale analyses of forest C cycling, we have developed an open-access Global Forest Carbon database, ForC (https://github.com/forc-db/ForC; Anderson-Teixeira et al 2016, 2018). ForC contains data on forest ecosystem C stocks and annual fluxes (>50 variables) and associated data required for interpretation (*e.g.*, stand history, measurement methods) amalgamated from numerous previous data compilations and directly from original publications. ForC currently contains **#** records from **#** plots and **#** distinct geographic areas representing all forested biogeographic and climate zones.

>>>>

                  \usepackage{setspace}\onehalfspacing
                  \usepackage{lineno}\linenumbers

@@

Despite the centrality of forest C cycling in regulating both atmospheric CO~2~ and ecosystem function and diversity, we lack a comprehensive understanding of how C cycling varies with across biomes and with stand age. While remote sensing measurements are increasingly useful for global- or regional-scale estimates of forest $GPP$ (Bagdley et al. 2019, [Li & Xiao 2019](https://www.mdpi.com/2072-4292/11/21/2563)), aboveground biomass ($B_{ag}$) (REFS), woody mortality (*i.e.*, $B_{ag}$ losses to mortality $M_{woody}$) ([Clark et al. 2004](https://www.onlinelibrary.wiley.com/doi/abs/10.1046/j.1461-0248.2003.00547.x); [Leithold et al 2018](https://nph-onlinelibrary-wiley-com.smithsonian.idm.oclc.org/doi/10.1111/nph.15110)), and to some extent net ecosystem exchange ($NEE$) (REFS), the remainder of C fluxes and stocks can only be quantified by ground-based measurements. Moreover, data on stand characteristics--including species composition, age, and disturbance history--are critical to interpreting and projecting into the future, but [usually rely on ground-based measurements]. Thus, ground-based measurements are--and will continue to be--central to characterizing forest C cycling. Tens of thousands of forest C measurements have been published, but their distribution across literally thousands of scientific articles-- along with variation in data formats, units, measurement methods, *etc.*--have made them effectively inaccesible for many global-scale analyses, including those attempting to quantify the role of forests in the global C cycle (*e.g.*, Pan et al 2011), and model evaluation (Clark et al 2017, Luo et al 2012). Important progress has been made in synthesizing data to address how C cycling varies across forest biomes (Luyssaert et al. 2007; REFS) and stand ages (REFS), yet generally consider only a limited set of C variables (but see Anderson-Teixeira et al 2016 for the tropics) and do not consider age-by-biome interactions. To address the need for global-scale analyses of forest C cycling, we have developed an open-access Global Forest Carbon database, ForC (https://github.com/forc-db/ForC; Anderson-Teixeira et al 2016, 2018). ForC contains data on forest ecosystem C stocks and annual fluxes (>50 variables) and associated data required for interpretation (*e.g.*, stand history, measurement methods) amalgamated from numerous previous data compilations and directly from original publications. ForC currently contains **#** records from **#** plots and **#** distinct geographic areas representing all forested biogeographic and climate zones.
